Type Refinements for the Working Class

### 2015-11-12 paper.tex
Add some spacing for Hom
Include pointful definitions
Fix up trailing space for Hom
Simplify definitions
Remove annotation
Fix inverted relation
Clearer name for the substitution of a mctx
"more recently" ⇒ "since the 1980s"

\newcommand\Hom[3]{#1\!\left[#2,#3\right]}

@@

Secondly, there is the view of type theory as semi-formal theory of
constructions for the Brouwer-Heyting-Kolmogorov interpretation of
intuitionistic mathematical language, which we will call \emph{behavioral} or
\emph{semantic type theory}. The most widely known development of this program
is Martin-L\"of's 1979 ``extensional'' type theory~\cite{martin-lof:1979,
martin-lof:1984}, but we must give priority to Dana Scott for inventing this
line of research in 1970 with his prophetic report, \emph{Constructive
Validity}~\cite{scott:1970}. More recently, behavioral type theory has been
developed much further in the Nuprl family~\cite{constable:1986} of proof
assistants, including MetaPRL~\cite{hickey:2003} and JonPRL~\cite{jonprl:2015}.

@@

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
   \[
     \textstyle
     \Define{
       \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
     }{
       \Hom{\mathbb{J}}{
         \Yoneda{w}
       }{
         Ran_{\mathbbold{1}}{\mathcal{J}}
       }
     }
   \]

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a section
   (i.e. for any substitution $\Member{\omega}{\square\Omega}$,
   $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us to
   quantify over terms of higher type.

@@

  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we can form the
  hypothetical judgment $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$, which expresses
  the semantic consequence of $\mathcal{J}_2$ from $\mathcal{J}_1$:
  \begin{align*}
    \ADefine{
      \left(\HypJ{\mathcal{J}_2}{\mathcal{J}_1}\right)(w)
    }{
      \left({\mathcal{J}_2}^{\mathcal{J}_1}\right)(w)
    }\\
    &\cong
    \OMode{
      \Hom{\mathbb{J}}{
        \Yoneda{w}\times\mathcal{J}_1
      }{
        \mathcal{J}_2
      }
    }
  \end{align*}

>>>>

\newcommand\Hom[3]{#1\!\left[#2,\,#3\right]\!}

@@

Secondly, there is the view of type theory as semi-formal theory of
constructions for the Brouwer-Heyting-Kolmogorov interpretation of
intuitionistic mathematical language, which we will call \emph{behavioral} or
\emph{semantic type theory}. The most widely known development of this program
is Martin-L\"of's 1979 ``extensional'' type theory~\cite{martin-lof:1979,
martin-lof:1984}, but we must give priority to Dana Scott for inventing this
line of research in 1970 with his prophetic report, \emph{Constructive
Validity}~\cite{scott:1970}. Since the 1980s, behavioral type theory has been
developed much further in the Nuprl family~\cite{constable:1986} of proof
assistants, including MetaPRL~\cite{hickey:2003} and JonPRL~\cite{jonprl:2015}.

@@

  For any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\square\Omega}}$, we can define
  the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows, where
  $\Of{\Yoneda{-}}{\mathcal{W}\to\mathbb{J}}$ is the Yoneda Embedding:
  \begin{align*}
    \ADefine{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        Ran_{\mathbbold{1}}{\mathcal{J}}
      }
    }\\
    &\cong
    \OMode{
      \int_{(w',\,\vec{E})}{{w'}\succeq{w}\Rightarrow{\mathcal{J}(\vec{E})(w')}}
    }
  \end{align*}

   Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
   when the family of judgments $\mathcal{J}$ shall forevermore have a section
   (i.e. for any substitution $\Member{\vec{E}}{\square\Omega}$,
   $\mathcal{J}(\vec{E})$ shall be evident). Recall that metavariables have
   \emph{valences} rather than sorts; as such, the general judgment allows us to
   quantify over terms of higher type.

@@

  For two judgments $\mathcal{J}_1$ and $\mathcal{J}_2$, we can form the
  hypothetical judgment $\HypJ{\mathcal{J}_2}{\mathcal{J}_1}$, which expresses
  the semantic consequence of $\mathcal{J}_2$ from $\mathcal{J}_1$:
  \begin{align*}
    \ADefine{
      \left(\HypJ{\mathcal{J}_2}{\mathcal{J}_1}\right)(w)
    }{
      \left({\mathcal{J}_2}^{\mathcal{J}_1}\right)(w)
    }\\
    &\cong
    \OMode{
      \Hom{\mathbb{J}}{
        \Yoneda{w}\times\mathcal{J}_1
      }{
        \mathcal{J}_2
      }
    }\\
    &\cong
    \OMode{
      \int_{w'}{{{w'}\succeq{w}}\Rightarrow{{{\mathcal{J}}_{2}(w')}^{{\mathcal{J}}_{1}(w')}}}
    }
  \end{align*}
